Place title here

### 2021-06-22 paper/Paper.tex

%header material for paper
\title{Relationships in the extremes and their influence on competition and coexistence}
\date{}

%Put other possible titles below, commented, and we will select the best one at the end
%Relationships between extreme events and their influence on competition and coexistence

@@

\begin{document}
\SweaveOpts{concordance=TRUE}

%The following is where you load in the numeric results that will be embedded in the text
<<eval=T,echo=F,message=F,warning=F>>=
system(paste("biber", sub("\\.Rnw$", "", current_input())))

#place R code here for loading in necessary variables from Results
#ordinarily this would be a readRDS command, but I'm just defining a variable here for now
allregres<-matrix(rnorm(10),2,5)
@

@@

\section{Theory}\label{section:theory}

@@

You can include the value of previously loaded R variables in the text, e.g., the value of allregres[1,5] is
\Sexpr{allregres[1,5]}, which can also be given rounded: \Sexpr{round(allregres[1,5],3)}. You can do simple R
on the fly, e.g., allregres[1,5] plus 1 is \Sexpr{allregres[1,5]+1}. 
You should never manually type any results, they should always be autolinks like this.

@@

%You make tables like this:
\begin{table}[H]
\caption[Summary caption, for table of contents, can be skipped.]{Full caption here.}
\begin{tabular}{llll} %The four ls mean four columns, each left justified. Can use r or c, too.
\hline 
Col 1 header & Col 2 header & Col 3 header & Col 4 header \\
\hline
text & or & numbers & 3.2 \\
or & math & $x+1$ & or \\
even & the & values & of \\
loaded & R & variables & \Sexpr{allregres[1,5]} \\
you & can & round & \Sexpr{round(allregres[1,5],3)} \\ 
\hline
\end{tabular}
\label{tab:random_table}
\end{table}

>>>>

%header material for paper
\title{Place title here}
\date{}

@@

\usepackage{Sweave}
\begin{document}
\input{Paper-concordance}

%The following is where you load in the numeric results that will be embedded in the text

@@

@@

You can include the value of previously loaded R variables in the text, e.g., the value of allregres[1,5] is
-1.16948109243002, which can also be given rounded: -1.169. You can do simple R
on the fly, e.g., allregres[1,5] plus 1 is -0.169481092430019. 
You should never manually type any results, they should always be autolinks like this.

@@

%You make tables like this:
\begin{table}[H]
\caption[Summary caption, for table of contents, can be skipped.]{Full caption here.}
\begin{tabular}{llll} %The four ls mean four columns, each left justified. Can use r or c, too.
\hline 
Col 1 header & Col 2 header & Col 3 header & Col 4 header \\
\hline
text & or & numbers & 3.2 \\
or & math & $x+1$ & or \\
even & the & values & of \\
loaded & R & variables & -1.16948109243002 \\
you & can & round & -1.169 \\ 
\hline
\end{tabular}
\label{tab:random_table}
\end{table}
